\documentclass[11pt]{article}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{times}
\usepackage{hyperref}
\hypersetup{hidelinks}

\begin{document}

\noindent 11 May 2026

\bigskip

\noindent Editorial Office \\
IEEE Access

\vspace{1.5em}

\noindent Dear Editorial Office,

\medskip

I am submitting the manuscript titled \textbf{``Beyond English-Only GRPO:
A Multi-Seed Empirical Study at Sub-3B Scale''} for consideration in
IEEE Access.

This work provides a multi-seed empirical study of Group Relative Policy
Optimization (GRPO) post-training of a 1.5B distilled reasoning model under
a single-GPU LoRA constraint. Building on the recent observation by
Hochlehnert et al.~(COLM 2025) that small-model RL reasoning gains may not
survive multi-seed evaluation, we test three training-condition arms across
three random seeds plus a single-seed mechanism ablation. The manuscript
makes four contributions:

\begin{enumerate}
\item Multi-seed empirical evidence that vanilla English GRPO at
sub-3B~$+$~LoRA scale exhibits $\sigma = 11.3$ percentage points (pp) seed
variance on AMC-23 and consistently degrades AIME-2024 pass@1, confirming
single-seed claims unreliable at this scale.

\item Documentation of the auxiliary-reward arm (A3) achieving the only
positive AIME-2024 maj@8 effect ($+4.4 \pm 1.9$\,pp over the untrained
base), robust across three seeds.

\item A constant-bias ablation (A4) that partially refutes a pure
reward-magnitude interpretation of the auxiliary-reward effect.

\item A 10-language MGSM evaluation showing null cross-lingual transfer
for all training conditions ($\pm 0.5$\,pp of base mean).
\end{enumerate}

The work fits IEEE Access's broad scope on engineering applications of
machine learning, with particular relevance to deployment-constrained
post-training of language models. Our reproducibility commitment (full
code released under Apache-2.0, LoRA adapters, evaluation JSONs with
SHA256 manifest, per-step training logs) addresses the IEEE emphasis on
rigorous and verifiable research.

In compliance with IEEE Access policies on AI-assisted academic work, the
manuscript and accompanying source code were prepared with assistance from
Anthropic Claude (via the Claude Code command-line interface). All
empirical results were independently produced and verified by the author,
who bears sole responsibility for the technical claims, methodology, and
any errors. The complete AI-assistance scope is detailed in the manuscript
and in the \texttt{VERIFICATION.md} audit document of the released
codebase.

The corresponding author and sole author is Vu Dang, an independent
researcher based in Vietnam. The work has not been published elsewhere and
is not under review at any other venue. Code and data are publicly
available at \url{https://github.com/vudang4494/xling-grpo-sub3b} and
permanently archived at Zenodo
DOI~\href{https://doi.org/10.5281/zenodo.20061328}{10.5281/zenodo.20061328}.

Thank you for your consideration.

\vspace{2em}

\noindent Sincerely,

\medskip

\noindent Vu Dang \\
Independent Researcher, Vietnam \\
\href{mailto:vu.dh4494@gmail.com}{vu.dh4494@gmail.com}

\end{document}
